%!TEX root = ../report.tex

% Include in your acknowledgements any person who has made a substantial contribution to your research, but doesn't qualify as an author. Examples include other students, staff, projects or organisations which have provided financial support or data.
% If you have questions about this please get in touch with your supervisor!


\begin{document}
\justifying

    \begin{acknowledgements}
         I would sincerely appreciate all of my supervisors for supporting me throughout my masters' studies and thesis period both technically and morally. The knowledge imparted by my professors at Hochschule Bonn Rhein Sieg has been boundless and second to none. Thanks for all the freedom and opportunities provided during this journey. I would also extend my appreciation to Iman, Alex, and Anastassia from Hochschule Bonn Rhein Sieg and Matias, Octavio from the German Research Center for Artificial Intelligence at Bremen for supporting me with the necessary infrastructure to accomplish my thesis work.
        
        Huge credit is due to my Mother, Sister, Brother-in-law, and the rest of family for supporting me through my masters' studies. Their motivation and perseverance through all the personnel losses during this period have been humbling and made me the considerate human that I am today. No words are sufficient to thank my father and mother who by God's grace are my first teachers and role models for all the discipline, ethics, and values they imparted in my life.
        
        The cities of Bonn and Cologne have provided me with a lot of memories. These cities are where I made many life-long friendships at the university and AKKA Technologies with Matthias, Santosh, Sasi, Lokesh, Ingrid, Ragith, Divin, and Alan. I really cannot thank you enough. I would like to extend my gratitude to all the front-line health workers, doctors, nurses, administration staff, and all the first responders during the corona pandemic times.
      
    \end{acknowledgements}
\end{document}
